Chronic imaging of cortical oxygen tension and blood flow after targeted vascular occlusion

### 2018-04-17 article.tex
Added Beer-Lambert explanation of wavelength discrepancies
Used rough Beer-Lambert Law calculations to estimate the transmission
of excitation light through surface vasculature to help explain the
differences between the 445 and 637 nm results.

The comparison of excitation wavelengths revealed significant differences in measured oxygen tension. Static \pO\ measurements under 445 nm illumination spanned a range five times larger than that of 637 nm illumination. This discrepancy was most noticeable in venous regions, with the shorter excitation wavelength resulting in \pO\ values around 50 mmHg whereas the longer wavelength resulted in values around 75 mmHg. Since depth penetration is heavily dependent upon wavelength\cite{Deng:2003kb,Davis:2011wj}, the difference is likely caused by excitation photons sampling a much larger volume of tissue under 637 nm illumination. The 445 nm light is more confined within the targeted vessel and does not sample as much of the surrounding parenchyma or deeper microvasculature. Because the 637 nm light penetrates further into the brain, the measured \pO\ is skewed away from the actual vascular value and is more representative of a bulk volumetric average. Despite this discrepancy, similar trends can be seen between the regions for both wavelengths with arterioles having higher \pO\ than veins or parenchyma.

>>>>

The comparison of excitation wavelengths revealed significant differences in measured oxygen tension. Static \pO\ measurements under 445 nm illumination spanned a range five times larger than that of 637 nm illumination. This discrepancy was most noticeable in venous regions, with the shorter excitation wavelength resulting in \pO\ values around 50 mmHg whereas the longer wavelength resulted in values around 75 mmHg. Since depth penetration is heavily dependent upon wavelength\cite{Deng:2003kb}, the difference is likely the result of photons sampling a much larger volume of tissue under 637 nm illumination. An estimate of transmission through a surface vessel at both wavelengths can be obtained using the Beer-Lambert Law. Because scattering increases the distance traveled by photons in tissue, this is the most conservative estimate of the effect of wavelength on transmission. Assuming hemoglobin is the primary absorber in blood plasma with a concentration of 2.3 mM \cite{Robles:2010cw} and 95\% SaO$_{2}$, the transmittance at 445 nm and 637 nm through a 100 $\mu$m arteriole is 0.9\% and 96.5\%, respectively. As excitation wavelength approaches the tissue optical window, the transmission of incident light significantly increases. The 445 nm light is almost entirely confined within a vessel of that caliber and does not extensively sample deeper microvasculature. Because the 637 nm light penetrates further into the brain, the measured \pO\ is skewed away from the vascular value and is more representative of a bulk volumetric average. This is consistent with prior Monte Carlo modeling that found fluorescence primarily originates from within surface vasculature at shorter wavelengths \cite{Davis:2011wj}.
